DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-25 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
% Include other packages here, before hyperref.

% https://tex.stackexchange.com/questions/251186/is-there-a-way-to-toggle-comments
% If there is always a blank line after then you could do (untested)
% below will swallow the comment
\def\tcom#1\par{}
% below will show the comment
%\def\tcom#1{}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3790} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}
%%%%%%%%% TITLE - PLEASE UPDATE
\title{DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving}  % **** Enter the paper title here

@@

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We would first like to thank the reviewers for the supportive comments and the constructive criticism. Your valuable feedbacks help us further improve the analysis of the proposed method and the overall presentation of the paper.
Due to the significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{https://drive.google.com/open?id=18RwGHG-Rbwfv-4bwmjjSfSl9jAHI-vbM}{new version of the paper}.

% Because of the space constraint we address only the major comments below.

\noindent \textbf{Modifications:} In what follows, we give an overview of the main changes made to the manuscript.

\noindent (1) We have implemented SocialLSTM[2] as requested by R2 and preliminary results on 2D space exhibit that the ``social interaction" further improve the prediction accuracy.

\noindent (2) We have restructured our methodology in section 3 and further explain the intuition behind the chosen architectures.

\noindent (3) We have rewritten our contributions in Section 1 and make our contributions more clearly.

\noindent \textbf{Common issues:} We would like to address the issues that are common to reviewers respectfully as follows:

\tcom 
\noindent \textbf{R1: Unlike stated in the paper, vehicle tracking in images has been studied for years. There are summary papers (e.g. VEHICLE DETECTION AND TRACKING TECHNIQUES: A CONCISE REVIEW Raad Ahmed Hadi1,2 , Ghazali Sulong1 and Loay Edwar George, SIPIJ). There is no mention of prior art.}
\noindent \textbf{R1: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
\noindent \textbf{R2: Where are comparisons with other activity forecasting/trajectory prediction works?}

\noindent \textbf{Prior works on sequence prediction}:
We found that the first version of the draft is indeed weak in presenting prior works on sequence prediction. We have restructured our related works. Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``Activity forecasting" part.

\tcom 
\noindent \textbf{R1: It is not clear if the dataset is released with the paper.}
\noindent \textbf{R2: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
\noindent \textbf{R2: Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}

\noindent \textbf{SYNTHIA and release of the dataset}:
\noindent Currently, experiments on the SYNTHIA dataset[27, 37] focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize \emph{continuous video streams} for the prediction problem. We would like to release publicly-available dataset for prediction challenge based on SYNTHIA to spur future research upon paper publication.

\tcom 
\noindent \textbf{R1: They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
\noindent \textbf{R2: I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?}
\noindent \textbf{R3: Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}

We would like to address the concerns respectfully as follows:
%####################################################################################################################################################################################
\noindent \textbf{R1}
\noindent \textbf{3) 3 very similar LSTMs with different input}
\noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}

%####################################################################################################################################################################################

\noindent \textbf{R2}

@@

 \noindent \textbf{Can multiple objects be tracked at once, or just one? The video in the supplementary material only showed one object being tracked. What was the average number of objects in each SYNTHIA scene frame?}

 \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to “predict car’s future odometry given previous egomotion visual input”. But the paper is about prediction of other vehicles’ trajectories, not about predicting one’s own car odometry (which is different).}

\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}

%####################################################################################################################################################################################

\noindent \textbf{R3}
\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here. In general a lot of methodology detail is actually in section 4 (implementation details). Maybe consider reorganizing a little bit.}

### 2018-01-25 paper/cvpr2018/cvpr2018_3790.tex
Rebuttal

\noindent \textbf{Datasets for autonomous driving} Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community.
CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV} are two recent endeavours that take advantage of simulated environment to support development, training and validation of autonomous urban driving systems.
A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is collected for investigating how useful synthetic images can be for semantic segmentation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\vspace{\baselineskip}
\noindent \textbf{Social tensor:} was firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space. Naturally, in the context of autonomous driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories. The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors. While pooling the information, the spatial information is preserved by grid based pooling. The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene. This representation can be shared with neighbors by building a social hidden tensor $s^i_t$:
\begin{equation}
s^i_t = \sum_{j \in \mathcal{N}_i} \mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t] \centerdot  h^j_{t-1}
\label{eq:social_tensor}
\end{equation}
where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to target $i$. 
The trajectory  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, s^i_H): \mathcal{J_H}  \times \mathcal{S}
\label{eq:FtS}
\end{equation}
This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM and training can be formulated as a neighboring batch update scheme. An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer. At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene.

@@

%%%%%%%%%%%%%%%%%
\begin{table}[t]
\small
   \centering
        %\begin{tabular}{|l *{2}{c}|}\hline
        %\begin{tabu}{|l *{2}{c}|}
        \begin{tabu}{@{}ccc@{}}\toprule
        [-1pt] \tabucline[1pt]{1-3}
                                                    &   Ave. disp. error      & Final disp. error   \\ \hline
            {\small Vanilla LSTM }                 &    0.0257                &  0.0440   \\
            {\small \textbf{Social LSTM} }         &  \textbf{0.0247}         & \textbf{0.0418}   \\
          [-1pt] \tabucline[1pt]{1-3}
        \end{tabu}
        %\end{tabular}

@@

\begin{table*}\centering
\small{
\ra{1.}
%\begin{tabular}{@{}llllllllllll@{}}\toprule
\begin{tabu}{@{}llllllllllll@{}}\toprule
[-1pt] \tabucline[1pt]{1-12}
\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
\hline
\multirow{3}{*}{Faster-RCNN}
                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
                    \cline{2-12}
\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
                    \cline{2-12}
\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\

\bottomrule
\end{tabu}
%\end{tabular}
\caption{
Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
It can be seen that:
(1) both meta-architectures are robust to the cut-off confident thresholds.
(2) SSD is more competitive in the collected dataset when targets of interest are large.
}
\label{tab:ssd_fasterrcnn}
}
\end{table*}

%
%\begin{table}[H]\centering
%\small{
%\ra{1.}
%%\begin{tabular}{@{}llllllllllll@{}}\toprule
%\begin{tabu}{@{}lllll@{}}\toprule
%[-1pt] \tabucline[1pt]{1-5}
%\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
%\multirow{3}{*}{Faster-RCNN}
%                                &   precision & 81.2    & 81.1  & 80.0\\
%                                &   recall    & 91.4    & 91.3  & 90.2\\
%                                &   f-score   & 86.0    & 86.0  & 84.8\\
%                                    \cline{2-5}
%\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
%                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
%                                &   f-score   & 87.1 &86.5  &84.0\\
%                                    \cline{2-5}
%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
%                                &   recall  & 92.3 & 91.4 & 87.7\\
%                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
%\bottomrule
%\end{tabu}
%%\end{tabular}
%\caption{
%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
%It can be seen that:
%(1) both meta-architectures are robust to the cut-off confident thresholds.
%(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
%}
%\label{tab:ssd_fasterrcnn}
%}
%\end{table}

@@

\section{2D and 3D occupancy grid}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
        \caption{
        \small{The evaluation of 2D and 3D prediction. 2D: The bounding box is set to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict 3D occupancy.}
        }
        \label{fig:evaluation}
\end{figure}

>>>>

\noindent \textbf{Datasets for autonomous driving} Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community.
CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV} are two recent endeavours that take advantage of simulated environment to support development, training and validation of autonomous urban driving systems.
A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark, HernandezBMVC17} is collected for investigating how useful synthetic images can be for semantic segmentation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\vspace{\baselineskip}
\noindent \textbf{Social tensor:} was firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space. Naturally, in the context of autonomous driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories. The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors. While pooling the information, the spatial information is preserved by grid based pooling. The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene. This representation can be shared with neighbors by building a social hidden tensor $s^i_t$:
\begin{equation}
s^i_t = \sum_{j \in \mathcal{N}_i} \mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t] \centerdot  h^j_{t-1}
\label{eq:social_tensor}
\end{equation}
where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to target $i$. 
The trajectory  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, s^i_H): \mathcal{J_H}  \times \mathcal{S}
\label{eq:FtS}
\end{equation}
This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM. An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer. At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.

@@

%%%%%%%%%%%%%%%%%
\begin{table}[t]
\small
   \centering
        %\begin{tabular}{|l *{2}{c}|}\hline
        %\begin{tabu}{|l *{2}{c}|}
        \begin{tabu}{@{}ccc@{}}\toprule
        [-1pt] \tabucline[1pt]{1-3}
                                                    &   Ave. disp. error      & Final disp. error   \\ \hline
            {\small Vanilla LSTM }                 &     0.0514              &  0.0880   \\
            {\small \textbf{Social LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
          [-1pt] \tabucline[1pt]{1-3}
        \end{tabu}
        %\end{tabular}

@@

%\begin{table*}[H]\centering
%\small{
%\ra{1.}
%%\begin{tabular}{@{}llllllllllll@{}}\toprule
%\begin{tabu}{@{}llllllllllll@{}}\toprule
%[-1pt] \tabucline[1pt]{1-12}
%\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
%\hline
%\multirow{3}{*}{Faster-RCNN}
%                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
%                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
%                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
%                    \cline{2-12}
%\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
%                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
%                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
%                    \cline{2-12}
%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
%                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
%                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
%
%\bottomrule
%\end{tabu}
%%\end{tabular}
%\caption{
%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
%It can be seen that:
%(1) both meta-architectures are robust to the cut-off confident thresholds.
%(2) SSD is more competitive in the collected dataset when targets of interest are large.
%}
%\label{tab:ssd_fasterrcnn}
%}
%\end{table*}

\begin{table}[H]\centering
\small{
\ra{1.}
%\begin{tabular}{@{}llllllllllll@{}}\toprule
\begin{tabu}{@{}lllll@{}}\toprule
[-1pt] \tabucline[1pt]{1-5}
\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
\multirow{3}{*}{Faster-RCNN}
                                &   precision & 81.2    & 81.1  & 80.0\\
                                &   recall    & 91.4    & 91.3  & 90.2\\
                                &   f-score   & 86.0    & 86.0  & 84.8\\
                                    \cline{2-5}
\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
                                &   f-score   & 87.1 &86.5  &84.0\\
                                    \cline{2-5}
\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
                                &   recall  & 92.3 & 91.4 & 87.7\\
                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
\bottomrule
\end{tabu}
%\end{tabular}
\caption{
Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
It can be seen that:
(1) both meta-architectures are robust to the cut-off confident thresholds.
(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
}
\label{tab:ssd_fasterrcnn}
}
\end{table}

@@

\section{2D and 3D occupancy grid}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
        \caption{
        \small{The evaluation of 2D and 3D prediction. 2D: The bounding box is set to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict 3D occupancy.}
        }
        \label{fig:evaluation}
\end{figure}
